Visualizations for the manuscript

### 2022-03-31 metanalysis_visualization/manuscript_Figures.Rmd
ongoing ITS changes

### Sex Summary
```{r}
sexInfo_per_country <- table1_all %>%
  filter( Category == "Sex") %>%
  mutate ( counts_before = as.numeric(sapply(strsplit( as.character(before_pandemic), " "), '[', 1)), 
           counts_during = as.numeric(sapply(strsplit( as.character(during_pandemic), " "), '[', 1))) %>%
  select( name, siteid, counts_before, counts_during ) %>%
  inner_join( country_map ) %>%
  group_by( name, country ) %>%
  summarise( before = sum( counts_before), 
             during = sum( counts_during )) %>%
  pivot_longer(names_to = "period", cols=c(before, during))

#patients_hospitalized_agg_sex_country <- patients_hospitalized_agg_sex_perc_all %>%
#  select( - percentage ) %>%
#  inner_join( country_map ) %>%
#  group_by( time_p, sex, country ) %>%
#  mutate( total_cases = sum( count ), 
#          sex_cases = sum( count_sex ), 
#          percentage = 100* sex_cases / total_cases) %>%
#  rbind( patients_hospitalized_agg_sex_total)

# patients_hospitalized_agg_sex_country %>%
#   ggplot( aes( x= as.Date( time_p ), y = percentage, group = sex )) +
#   geom_line( aes(linetype = sex, color = sex )) +
#   geom_point( aes( shape= sex, color = sex )) +
#   scale_colour_manual(values=c("#FF6600","#339999")) +
#   scale_fill_manual(values=c("#FF6600","#339999"))+
#   #scale_y_continuous(breaks = seq(0, 30, by = 1)) +
#   facet_wrap2("country", axes = "all") + 
#   geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
#   labs(x ="", y = "percentage of patients (%)")+
#   scale_x_date(breaks = "2 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
#   theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
#         strip.text = element_text(size = 10, face = "bold"),
#         panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
#         panel.border = element_rect(colour = "black", fill = NA), 
#         legend.position="bottom")
```

@@

## Recompute the bootstrap

@@

bootstrapping_slopes <- function(patient_count_psy_period_psy, 
                                    bootstrap_size) {
  bootstrapped_timepoints <- mapply(binom_proportion,
                                    n = bootstrap_size,
                                    size = patient_count_psy_period_psy$count_no_psy_patients +
                                      patient_count_psy_period_psy$count_psy_patients,
                                    prob = patient_count_psy_period_psy$percentage/100)
  bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
  bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
  for (iteration in 1:bootstrap_size) {
    df_iteration <- data.frame(period = patient_count_psy_period_psy$period,
                               time = patient_count_psy_period_psy$time,
                               percentage = bootstrapped_timepoints[iteration, ])
    ts_linear_percent <- lm(percentage ~ period * time, df_iteration)
    linear_model <- broom::tidy(ts_linear_percent) %>%
      filter(term %in% c("time", "periodduring_pandemic:time"))
    coefficients <- linear_model$estimate
    names(coefficients) <- linear_model$term
    bootstrapped_coefficients_list[[iteration]] <- coefficients
    df_iteration$predicted <- predict(ts_linear_percent)
    df_iteration$time_p <- patient_count_psy_period_psy$time_p
    bootstrapped_sample_list[[iteration]] <- df_iteration
  }
  bootstrapped_fitted_df <- bind_rows(bootstrapped_sample_list, .id = "iteration")
  bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list,
                                          .id = "iteration")
  return(list(bootstrapped_coefficients_df, 
              bootstrapped_fitted_df))
}
```

```{r}
# Get count_icd_all in the same format that patient_count_psy_period_psy_all, because first n last months missing ... 
count_icd_all_boot <- count_icd_all %>% 
  group_by(siteid) %>% # necessary to generate time correctly 
  rename(count_psy_patients = count_psy, 
         percentage = percentage_psy) %>% 
  mutate(count_no_psy_patients = count_icd - count_psy_patients, 
         month_year = format(time_p, "%m"),
         time = seq_along(time_p))

bootstrapped <- count_icd_all_boot %>% 
  group_by(siteid) %>% 
  group_map( ~bootstrapping_slopes(.x, bootstrap_size = bootstrap_size))
names(bootstrapped) <- unique(count_icd_all$siteid)

@@

```{r}
quantile_bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  group_by(time_p, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

annotation_function <- function(df, ...) {
  z <- unique(df[["observed_diff"]]) / sd(df[["periodduring_pandemic:time"]])
  pvalue_coeff_interaction = round(pnorm(abs(z), lower.tail = FALSE) * 2, 3)
  paste0("Coeffs differences: ",
         round(unique(df[["observed_diff"]]), 2),
         " (pvalue: ",
         pvalue_coeff_interaction,
         ")")
}

df_coefficients_boot <- bootstrapped_coefficients_all %>% 
  left_join(coefficients_df, by = "siteid")

@@

```{r}
# Random effect effects
model_meta_siteid <- metafor::rma(yi = observed, 
                                  vi = var_boot,
                                  measure = "MN",
                                  method = "DL",
                                  data = trends_siteid)

@@

>>>>

@@

## Define bootstrap functions

@@

bootstrapping_slopes <- function(df, 
                                 bootstrap_size, 
                                 count = "count_icd", 
                                 percentage = "percentage", 
                                 group_name = .y) {
  bootstrapped_timepoints <- mapply(
    binom_proportion,
    n = bootstrap_size,
    size = df[[count]],
    prob = df[[percentage]]/100)
  bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
  bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
  for (iteration in 1:bootstrap_size) {
    df_iteration <- data.frame(period = df$period,
                               time = df$time,
                               percentage = bootstrapped_timepoints[iteration, ])
    ts_linear_percent <- lm(as.formula(paste0(percentage, "~ period * time")), df_iteration)
    linear_model <- broom::tidy(ts_linear_percent) %>%
      filter(term %in% c("time", "periodduring_pandemic:time"))
    coefficients <- linear_model$estimate
    names(coefficients) <- linear_model$term
    bootstrapped_coefficients_list[[iteration]] <- coefficients
    df_iteration$predicted <- predict(ts_linear_percent)
    df_iteration$time_p <- df$time_p
    bootstrapped_sample_list[[iteration]] <- df_iteration
  }
  bootstrapped_fitted_df <- bind_rows(bootstrapped_sample_list, .id = "iteration") %>% 
    mutate(group = group_name)
  bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list,
                                          .id = "iteration") %>% 
    mutate(group = group_name)
  return(list(bootstrapped_coefficients_df, 
              bootstrapped_fitted_df))
}
```

```{r}
# Get count_icd_all in the same format that patient_count_psy_period_psy_all, because first n last months missing ... 
count_icd_all_boot <- count_icd_all %>% 
  group_by(siteid) %>% # necessary to generate time correctly 
  rename(percentage = percentage_psy) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))

bootstrapped <- count_icd_all_boot %>%
  group_by(siteid) %>% 
  group_map( ~bootstrapping_slopes(.x, bootstrap_size = bootstrap_size))
names(bootstrapped) <- unique(count_icd_all_boot$siteid)

@@

```{r}
annotation_function <- function(df, ...) {
  z <- unique(df[["observed_diff"]]) / sd(df[["periodduring_pandemic:time"]])
  pvalue_coeff_interaction = round(pnorm(abs(z), lower.tail = FALSE) * 2, 3)
  paste0("Coeffs differences: ",
         round(unique(df[["observed_diff"]]), 2),
         " (pvalue: ",
         pvalue_coeff_interaction,
         ")")
}
```

```{r}
quantile_bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  group_by(time_p, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")
```

```{r}
df_coefficients_boot <- bootstrapped_coefficients_all %>% 
  left_join(coefficients_df, by = "siteid")

@@

```{r}
# Random effect
model_meta_siteid <- metafor::rma(yi = observed, 
                                  vi = var_boot,
                                  measure = "MN",
                                  method = "DL",
                                  data = trends_siteid)

@@

### Sex Summary

```{r}
sexInfo_per_country <- table1_all %>%
  filter( Category == "Sex") %>%
  mutate ( counts_before = as.numeric(sapply(strsplit( as.character(before_pandemic), " "), '[', 1)), 
           counts_during = as.numeric(sapply(strsplit( as.character(during_pandemic), " "), '[', 1))) %>%
  select( name, siteid, counts_before, counts_during ) %>%
  inner_join( country_map ) %>%
  group_by( name, country ) %>%
  summarise( before = sum( counts_before), 
             during = sum( counts_during )) %>%
  pivot_longer(names_to = "period", cols=c(before, during))

```{r Interrupted time series by sex}

  # pivot_wider(names_from =  sex, values_from = c(count, percentage))
  # group_by(siteid) %>% # necessary to generate time correctly 
  # rename(count_psy_patients = count_psy, 
  #        percentage = percentage_psy) %>% 
  # mutate(count_no_psy_patients = count_icd - count_psy_patients, 
  #        month_year = format(time_p, "%m"),
  #        time = seq_along(time_p))

bootstrap_size = 10

patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc_all %>% 
  mutate(period = ifelse(time_p <= as.Date("2020-03-15"), "before_pandemic", "during_pandemic")) %>% 
  select(time_p, period, sex, count, percentage, siteid)

bootstrapped_sex <- patients_hospitalized_agg_sex_perc_all %>%
  group_by(siteid, sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
 group_map( ~bootstrapping_slopes(.x, bootstrap_size = bootstrap_size, count = "count"))
names(bootstrapped_sex) <- unique(patients_hospitalized_agg_sex_perc_all$siteid)

bootstrapped_coefficients_sex <- lapply(bootstrapped_sex, `[[`, 1) %>% bind_rows(.id = "siteid")
bootstrapped_fitted_sex <- lapply(bootstrapped_sex, `[[`, 2) %>% bind_rows(.id = "siteid")

quantile_bootstrapped_fitted_sex <- bootstrapped_fitted_sex %>%
  group_by(time_p, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

```{r}
coefficients_df_sex <- patients_hospitalized_agg_sex_perc_all %>% 
  group_by(siteid, sex) %>% 
    mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_modify(coefficient_slope_calculation) %>% 
  rename(observed_diff = estimate)

```{r}
df_coefficients_boot_sex <- bootstrapped_coefficients_sex %>% 
  left_join(coefficients_df_sex, by = c("siteid", "sex"))
```

```{r}
names_site_id <- unique(df_coefficients_boot_sex$siteid)

plot_annotations <- df_coefficients_boot_sex %>% 
  group_by(siteid, sex) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_site_id) %>% 
  unlist()
plot_annotations_df <- data.frame(
  siteid = names(plot_annotations), 
  label = plot_annotations
)
```
